NMRlipids Databank: Overlay Databank of Lipid Membrane Simulations Arising from Open Collaboration

### 2022-04-03 Manuscript/main.tex
Updates from Overleaf

>>>>

\begin{figure}
    \centering
    \includegraphics[width=180mm]{Figures/quality.pdf}
    \caption{Caption}
    \label{fig:quality}
\end{figure}

The top ranking simulations according to the NMRlipids measures are shown in Fig.~\ref{fig:quality}. The overall best ranking simulation, POPC lipid bilayer simulated with Slipids force field, gives a good agreement with experiments for all C-H bond order parameters except for glycerol backbone. The best simulation for headroup and glycerol backbone, CHARMM36 POPC, predicts too ordered acyl chain, thereby not being within the top 10 simulations in the overall ranking. The best ranking for x-ray form factor is given by the Slipids POPE simulation, however, because the quantitative value for form factor quality depends on the quality of experimental data, form factor qualities can be compared only between simulations evaluated against the same experimental dataset.
